Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-31 bbbq_article.tex
Add plot of old study for comparison, progress #203
Add plot of old study for comparison, fix #203

This study differs in one important aspect from our previous work (\cite{bianchi2017}), 
The definition of a binder differs from \cite{bianchi2017}:
in the current study a peptide is called a binder if, within a certain haplotype, 
any of its 9-mer peptides have an IC50 value in the lowest 2\% of 
the epitopes within a 
\emph{proteome} (see tables \ref{tab:ic50_binders_mhc1} and \ref{tab:ic50_binders_mhc2}
for values), whereas the original study defined
a binder as having an IC50 in the lowest 2\% 
of the peptides within a \emph{protein}, 
which put less strain on the bioinformatics pipeline.
% See https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/72e6755a31d400158368509fd80a41e984677ab1/predict-binders.R#L17
\richel{Show side-by-side-comparison in supplementary materials}
We believe that our revised definition precludes bias of proteins 
that give rise to no or only very few MHC epitopes

@@

>>>>

This study differs in one important aspect from our previous work (\cite{bianchi2017}), 
The definition of a binder differs from \cite{bianchi2017}:
in the current study a peptide is called a binder if, within a certain haplotype, 
any of its 9-mer peptides have an IC50 value in the lowest 2\% of 
the epitopes within a 
\emph{proteome} (see tables \ref{tab:ic50_binders_mhc1} and \ref{tab:ic50_binders_mhc2}
for values), whereas the original study defined
a binder as having an IC50 in the lowest 2\% 
of the peptides within a \emph{protein}, 
which put less strain on the bioinformatics pipeline.
% See https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/72e6755a31d400158368509fd80a41e984677ab1/predict-binders.R#L17
We believe that our revised definition precludes bias of proteins 
that give rise to no or only very few MHC epitopes.
To verify our results are similar,
we compare the previous and the
current approach side by side in the supplementary materials.

@@

% \paragraph{Compare results in figure}

To verify if the previous and the current method give rise to
notable difference, we show a side-by-side comparison
in figures \ref{fig:bianch_et_al_2017_1a} and \ref{fig:bilderbeek_et_al_2021_1a}.
The figures that haplotypes that over-present or under-present TMH-derived epitopes,
do so in both studies. The extent to which TMH-derived eptitopes are
presented, however, is more extreme in our current setup.

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bianchi_et_al_2017_results/fig_1a.png}
    \label{fig:bianch_et_al_2017_1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_2_human_mhc1.png}
    \label{fig:bilderbeek_et_al_2021_1a}
  \end{subfigure}

  \caption{
    \textbf{(A)} 
    Results for \cite{bianchi2017}. 
    Red lines denotes the coincidence interval.
    \textbf{(B)}
    Results for this study.
    Red line denotes the percentage as expected by chance.
  }
\end{figure}
